C2H-

### 2022-03-01 Letter.tex
upload paper to git

As the radial dipole matrix elements will vary with electron kinetic energy, so too will $\beta$. Therefore, measuring anisotropy parameters at a range of energies will reveal the character of the detachment orbital. Anisotropy parameters were calculated for all resolved transitions in the C$_2$H$^-$ photoelectron spectra from $266-355$~nm, as shown in Fig.~\ref{fig:4}.

@@

Therefore, calculating the anisotropy parameter for a given transition will reveal the symmetry of the state, which can be compared to the symmetry of the calculated vibronic levels. However this is complicated by the presence of HT coupling, which allows for the electronic character of two surfaces to be mixed via a vibrational promoting mode. As shown in the Supplementary Materials, the transition dipole moment for a HT coupled transition may be rewritten as
\begin{align}
\mu_{\alpha}^{a-n} &= \langle \Psi_{\text{anion}}|\vec{\mu_{\alpha}}|\Psi_{\text{neutral}}\rangle\\
&= \mu_{\alpha:0}^{\tilde{X}-\tilde{X}}\langle\chi_{ms}''|\chi_{jt}'\rangle+\gamma_{kr,jt}\mu_{a:0}^{\tilde{A}-\tilde{X}}\langle\chi_{ms}''|Q_n|\chi_{kr}'\rangle
\label{eq:1}
\end{align}  
where $\mu_{\alpha:0}^{\tilde{X}-\tilde{X}}$ and $\mu_{a:0}^{\tilde{A}-\tilde{X}}$ are the electronic transition moments for the $\tilde{X}\leftarrow\tilde{X}$ and $\tilde{A}\leftarrow\tilde{X}$ transitions, $\chi_{ms}'',~\chi_{jt}',~$and$~\chi_{kr}'$ are the nuclear components of the anion and neutral respectively, and $\gamma_{kr,jt}$ is the vibronic coupling constant. Therefore, HT coupled transitions on the $\tilde{X}^2\Sigma^+$ surface are expected to have anisotropy parameters that reflect the coupled $\tilde{A}^2\Pi$ surface.

Anisotropy parameters were calculated for all strong transitions in the C$_2$H$^-$ photoelectron spectra from $355-266$~nm, as shown in Fig.~\ref{fig:4}.

>>>>

As the radial dipole matrix elements will vary with electron kinetic energy, so too will $\beta$. Therefore, measuring anisotropy parameters at a range of energies will reveal the character of the detachment orbital. Anisotropy parameters were calculated for all resolved transitions in the C$_2$H$^-$ photoelectron spectra from $266-355$~nm, and for C$_2$D$^-$ at 355~nm ,as shown in Fig.~\ref{fig:4}.

\begin{figure}
	\includegraphics[width=0.6\textwidth]{figures/PAD}
	\caption{cat}
	\label{fig:4}
\end{figure}

@@

Equation~(\ref{eq:beta-sanov}) may be fitted to the experimental anisotropy parameters in Fig.~\ref{fig:4} to determine the orbital character and Hanstorp coefficients. All transitions to the $\tilde{A}^2\Pi$ surface may be described by detachment from an orbital with 90\% $s$ character, and a Hanstorp coefficient of A=1.5(4)~eV$^{-1}$. However describing transitions to the $\tilde{X}^4\Sigma^+$ surface is complicated by the presence of HT coupling, which allows for the electronic character of two surfaces to be mixed via the promoting $v_2$ mode. The non-coupled allowed transitions may be described by detachment from an orbital with 90\% $p$ character, and a Hanstorp coefficient of A=0.66(4)~eV$^{-1}$. However the forbidden 2$^{2n+1}$ transitions follow the $s$-like detachment of the excited state. Therefore, measuring the anisotropy parameter of transitions near the conical intersection, where transitions to both surfaces overlap, will determine the symmetry of each level. This can then be compared to the calculated vibronic levels of Ref.** to help assign the transitions, as shown in Table~S1 and S2.

\subsection{Coupling Calculations}
In order to investigate the role of C$_{2n}$H and C$_{2n}$H$^-$ species in interstellar chemistry, theoretical approaches are required to link the terrestrial laboratory studies to astronomical observations. In particular, the ability to simulate electronic absorption spectra under interstellar conditions is required to survey potential DIB carriers. However the strong vibronic coupling in C$_{2n}$H species that has been explored in this study, makes these calculations exceedingly difficult.

Here, we show how the photoelectron spectrum of C$_2$H$^-$, including vibronic coupling effects, may be simulated using a quasidiabatic Hamiltonian. Complications brought about by the vibronic interactions between the strongly coupled $\Sigma^+$ and $\Pi$ states in the adiabatic representation can be avoided - in principle - via a transformation to a diabatic model. A useful diabatic nuclear kinetic energy operator may be achieved by representing the wavefunction of the molecule as a product of the electronic wavefunction with electronic coordinates at a frozen reference geometry, and vibrational wavefunction
\begin{equation}
\Psi_{\text{diabatic}} = \psi_{0} \chi.
\end{equation}
The electronic states responsible for the failure of the adiabatic model may be isolated (in the diabatic basis) from the rest of the electronic states (in the adiabatic basis). This mixing of states prevents the electronic Hamiltonian from being strictly diagonal. However, if the frozen electronic states are well-chosen, then the off-diagonal terms in the kinetic
energy operator are small and can be effectively neglected. This resulting electronic basis is the quasidiabatic representation.

\begin{equation*}
\boldsymbol{V} = 
\begin{pmatrix}
\Delta_0^X + \sum\limits_i F^{X}_{i}q_{i} + \frac{1}{2}\sum\limits_i F^{X}_{ij}q_{i}q_{j}  &
\sum\limits_i \lambda_{i}^{XA}q_{i} \\
\sum\limits_i \lambda_{i}^{AX}q_{i} &
\Delta_0^A + \sum\limits_i F^{A}_{i}q_{i} + \frac{1}{2}\sum\limits_i F^{A}_{ij}q_{i}q_{j} \\  
\end{pmatrix}
\end{equation*}

The diagonal terms of $\boldsymbol{V}$ represent the quasidiabatic potential energy surfaces, and contain force constants F associated with the normal modes i,j. $\Delta_0$ is the vertical electron detachment energy from C2H$^-$ to the neutral $\tilde{X}^2\Sigma^+$ ground state of C2H, denoted X, and the low-lying $\tilde{A}^2\Pi$ excited state, denoted A.  
The off-diagonal terms of $\boldsymbol{V}$ contain the coupling constants between the quasidiabatic electronic states, $\lambda$.
The adiabatic potential energy surfaces, $\nu_x$ and $\nu_a$, are obtained through the diagonalization of $\boldsymbol{V}$ and are equal to the quasidiabatic surfaces at a reference geometry, $R_0$. Additionally, this applies to all structures displaced from $R_0$ along totally symmetric coordinates, but loses this correspondence along coupling coordinates, particularly at a conical intersection. 
Therefore, all force constants in the diagonal blocks of $\boldsymbol{V}$ in the quasidiabatic representation that are associated with totally symmetric coordinates are equivalent to those obtained in the adiabatic representation and, thus, can be generated using standard ab initio quantum-chemical calculations.

\begin{equation*}
F^X_i = \left(\frac{\delta\nu}{\delta q_i}\right)_{R_0} ; \quad F^X_i = \left(\frac{\delta\nu^2}{\delta q_i\delta q_j}\right)_{R_0} ;\quad ...
\end{equation*}

\begin{equation*}
\forall i,j...\in\Gamma{_tot.symm.},
\end{equation*}

For the case in which the normal modes, ij, correspond to coupling modes, the diabatic force constants $F_{ij}$ and the adiabatic force constants are not equal due to the off-diagonal coupling terms, and are instead written

\begin{equation*}
F^{X(A)}_{ij} = f_{ij}^{X(A)} + \frac{2\lambda_{i}\lambda_{j}}{\Delta^{A(X)}_{X(A)}}, \quad \Delta^{A}_{B} = E_A - E_X,
\end{equation*}

where $F_{ij}$ and $f_{ij}$ are the quasidiabatic and adiabatic force constants, respectively. $\Delta^{A}_{X}$ is equal to the vertical energy difference between the coupled states X and A at the reference geometry. 
Furthermore, due to the large geometrical differences between the reference and final states, force fields are not calculated at the reference geometry -- on the adiabatic surface -- but rather, are calculated at the minima of the final states and are transformed into the basis of the reduced normal coordinates of the reference state. This is known as "adiabatic parametrization", and is necessary to generate reasonable diabatic force constants.

Lastly, the off-diagonal terms of $\boldsymbol{V}$ are the coupling constants between the vibronically mixed final states and were determined analytically. ***Need John's help...Did we do any transformation to make PJT quasidiabatic...***

The adiabatic potential energy surfaces were calculated using the coupled cluster
method with single, double and triple excitations (CCSDT). A restricted Hartree-Fock (RHF) reference function was used, along with the atomic natural orbital (ANO) basis set. The basis included...***help*** (ANO2). The geometries for each state were determined using a RHF-CCSDT/ANO2 optimization procedure based on analytic gradients. The quadratic force constants were calculated from harmonic frequency calculations based on analytic derivatives. The resulting coupling constants and force constants are presented in Table 1.

The resulting simulated spectrum is presented in Fig.~\ref{fig:5} alongside the experimental photoelectron spectrum.

Discuss difference in C2H and C2D...
